Implementing Capon Adaptive Beamforming on the GPU for Real Time Cardiac Ultrasound Imaging

### 2012-06-26 HRUIonGPU/jrnl_article.tex
Started incorparated comments from sverre++

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Adaptive beamforming, Capon beamformer, Graphics Processing Unit, GPGPU, Parallel Computing, Ultrasound Imaging.
\end{IEEEkeywords}

@@

%\IEEEPARstart{I}{ntroduction} to Capon adaptive beamforming, ultrasound imaging and GPU/CUDA.
\IEEEPARstart{C}{apon} adaptive beamforming applied in a medical ultrasound setting has recently shown promising results in several studies \cite{Synnevag2007, Austeng2008, Vignon2008, Viola, Mehdizadeh2012}. Although the method introduce some interesting trade-offs in addition to just improved resolution, like maintaining image resolution combined with higher framerates, smaller probes, or deeper penetration \cite{Synnevag2009}, widespread use has been limited by the tremendous computational complexity associated with the method \cite{So2011}.  In this paper we introduce the first implementation of the Capon beamformer exhibiting real-time performance when applied in a typical cardiac ultrasound setting. To accomplish this task we make use of the massive parallel processing power found in modern graphics processing units (GPU's), combined with novel methods to reduce the computational complexity as the problem size grows. Earlier attempts on real time Capon beamforming have been focused around radar and passive sonar systems using intricate systolic array processors \cite{McWhirter1989, Moonen1993, Sinha2002}.  A systolic array processor is custom made hardware, and even if the computational throughput might be higher for selected problems compared with a GPU, the cost related to development and flexibility is considered much higher. For medical ultrasound, Chen et al. \cite{Chen2011a, Chen2011} have previously implemented the Capon beamformer on a GPU, however their implementation was based on real data, where the Capon beamformer assumes complex. Using real data will results in symmetric windows, and even if the number of samples they managed to process per second was high, both the number of floating point operations per sample and the imaging region is reduced using real data compared with use of complex data. It is crucial to use complex data within the Capon beamformer framework, both for reducing the amount of data per image, and to allow for asymmetric windows. All results in this paper is reported with use of critically sampled complex data, both laterally and in range.

@@

\begin{figure*}[t!]
\centerline{\subfloat[]{\includegraphics[width=3in]{gfx/beamforming_mv_lowres.png} \label{fig:mvbf}}
\hfil
\subfloat[]{\includegraphics[width=3in]{gfx/gpu_layout_lowres.png}%
\label{fig:gpulayout}}}
\caption{a) Beamforming with adaptive weights $\vec{w}[n]$. Impinging signal is demodulated and aligned in phase by applying steering and focusing delays $\Delta_m[n]$. Capon adaptive weights are then calculated based on the in-phase data, and finally the output is formed by a weighted coherent sum. b) Calculation of Capon adaptive weights mapped to GPU architecture. A recorded echo across the array for a given range and angle (selected cell) is assigned to a group of $L$ threads that can run independently of all other groups. Note that several samples can be processed per block of threads if $L$ is small. The task of these $L$ threads is to calculate the Capon beamformer output in the three depicted steps.}
\label{fig:fig1}
\end{figure*}

\subsection{Capon Beamforming}
When sensing the world around us with an array of elements, we perform a spatio-temporal filtering operation known as beamforming. The conventional form of beamforming is delay-and-sum (DAS), where the signal recorded on each element, $x_m[n]$, is delayed to broadside with an appropriate delay $\Delta_m[n]$. The beamformer output, $z[n]$, is then the sum of all $M$ channels weighted with a factor $w_m$,
\begin{align}
z[n] = \sum_{m = 0}^{M-1}w_m^*x_m[n - \Delta_m[n]] = \vec{w}^H\vec{x}[n].
\end{align}
In conventional beamforming, the weighting $\vec{w}$ is usually real, and applied to trade resolution for a better signal-to-noise ratio (SNR). Hence, by increasing the main lobe width of the system while gaining lower side lobe levels.

The basic idea of an adaptive beamformer, as shown in Figure \ref{fig:mvbf}, is to calculate the weights on-the-fly, based on the data at hand, and on a selected optimization criteria in such a way that we minimize interference impinging from other directions than the point of focus. For a complex data vector $\vec{x}[n] \in \mathbb{C}^M$, we have for an adaptive beamformer a data-dependent set of weights, $\vec{w}(\vec{x}[n])$, that when applied on $\vec{x}[n]$ is the best approximation to achieving the selected criteria. With the Capon beamformer, adaptive weights are found by solving the following minimization problem \cite{Capon1969}:
\begin{align}
&\min_{\vec{w}} E\{|z[n]|^2\} = \min_{\vec{w}}\vec{w}^H\mat{R}\vec{w}\label{eq:minz}\\
&\text{subjected to } \vec{w}^H\vec{a} = 1,\label{eq:constraint}
\end{align}
where $\mat{R} = E\{\vec{x}[n]\vec{x}[n]^H\}$ is the spatial covariance matrix, and $\vec{a} = \left[ \begin{array}{cccc} e^{-jk_{\tilde{x}}\tilde{x}_0}& e^{-jk_{\tilde{x}}\tilde{x}_1}& ...& e^{-jk_{\tilde{x}}\tilde{x}_{M-1}}\end{array}\right] ^T$ is a far-field steering vector towards angle $\theta = \arcsin(\frac{\lambda k_{\tilde{x}}}{2\pi})$.
Thus, we minimize the output power, while maintaining unit gain in the look direction. The constraint in (\ref{eq:constraint}) is there to avoid the trivial solution $\vec{w} = 0$, and a distorted respons in the direction of $\vec{a}$. The solution to the minimization problem in (\ref{eq:minz}) and (\ref{eq:constraint}) is
\begin{align}\label{eq:w}
\vec{w}[n] = \frac{\mat{R}[n]^{-1}\vec{a}}{\vec{a}^H\mat{R}[n]^{-1}\vec{a}},
\end{align}
where $\vec{a} = [1_0 1_1... 1_{M-1}]^T = \vec{1}$ when $\vec{x}$ is pre-delayed to broadside.

@@

@@

\subsection{GPU Compute Model}
In this section we briefly discuss the principle behind GPU computing, laying the basis for further discussion on parallel implementation strategies. CUDA by Nvidia has been our choice of GPU developer environment \cite{Nvidia2011}. However, even though CUDA has been used to implement the Capon beamformer, the challenges and proposed methods described in this paper applies for other massive parallel implementation environments as well, like e.g. OpenCL.

@@

\section{Parallel Capon}\label{sec:meth}
As mentioned, widespread use of Capon adaptive beamforming has been limited by its computational complexity. However, the calculation of Capon weights is well suited for a GPU implementation, since the calculations are both independent across pixels, and partially intra-pixel. Based on memory dependencies it is trivial to recognise that one block of threads should process at least one pixel in the final image. Continuing, on a pixel-level, the algorithm can be broken down into three main steps that to some extent can be further divided into a small set of parallel processes. That is, for each data vector $\vec{x}$ in the image:
\begin{enumerate}
\item Calculate the sample covariance matrix $\mat{\hat{R}}$ as in (\ref{eq:R})
\item Solve the linear system of equations $\mat{\hat{R}}\vec{b} =\vec{ 1}$
\item Calculate $\vec{w} = \vec{b}/\vec{1}^H\vec{b}$ and the amplitude $\vec{w}^H\vec{x}$
\end{enumerate}
The computational complexity of these three steps, with $L = M/2$, is $O(L^3)$, $O(L^3)$, and $O(L)$ respectively. For larger $L$'s, the first two steps quickly becomes unmanageable, and real time performance can only be achieved by exploring novel solutions to reduce complexity.

(The three steps have, for modularity, been implemented using three different kernels. Joining all kernels into one could possible lead to an increase in speed.)

@@

\subsection{Calculating Multiple Sample Covariance Matrices}
The straight forward sum in (\ref{eq:R}) has complexity $O(L^2KN) = O(L^3)$ if $L$ is a small fraction of $M$. This is actually the same as for inverting a $L \times L$ matrix. However, little attention has been devoted to this step in the literature until now. Note that for a typical array configuration, N is usually small compared to L and M. Hence, for a small $L$ the construction of $\mat{\hat{R}}$ is dominated by $M$, since $K = M - L + 1$. From (\ref{eq:R}) it is obvious that calculation of one element in $\mat{\hat{R}}$ is independent of all the others. A natural level of granularity would then be to assign one thread to each element of $\mat{\hat{R}}$. This will minimize global reads and writes needed per thread, but unfortunately the maximum number of threads per block puts an upper limit on $L$, $L_{max}=32$, if we want to avoid block-to-block synchronization.

@@

@@

\subsection{Iterative Capon}
The idea behind iterative Capon is to perform Capon using small subarrays in several iterations until there is only two subarrays to sum. In this way we fix the size of L, hence the complexity of solving $\mat{R}\vec{b} = \vec{1}$. However, for each iteration we re-obtain L-1 degrees of freedom until all are retrieved after $K = M-L+1$ iterations. Since subarray averaging has been applied to decorrelated the signal, we might loose this effect when reestablishing all degrees of freedom. The number of iterations should therefore be restricted to $K/2$ to equal the normal choice of $L = M/2$ when it comes to degrees of freedom.

\subsection{Toeplitz-based solver} 
(cite new article). Discuss it.

@@

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_us_32_lr.png} \label{fig:benchUS32}}
\hfil
\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_us_64_lr.png}%
\label{fig:benchUS64}}}
\caption{Benchmark of GPU Capon beamforming for a cardiac image covering a 70 degrees sector. Execution time is plotted as a function of subarray length $L$. The plot shows execution times for the three steps listed in Section \ref{sec:meth}. Calculating covariance matrices in red, solver in green, and the final beamformer sum in blue. For each step, there is one line for three different choices of temporal averaging, $N_{avg} \in [0, 1, 2]$. (a) A 32 elements array. (b) A 64 elements array.}
\label{fig:bench}
\end{figure*}

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_us_32_lr.png} \label{fig:benchUS32}}
\hfil
\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_us_64_lr.png}%
\label{fig:benchUS64}}}
\caption{(TODO: Add the right figure) Benchmark of GPU Beamspace Capon beamforming for a cardiac image covering a 70 degrees sector. Execution time is plotted as a function of number of elements $M$. The plot shows execution times for the three steps listed in Section \ref{sec:meth}. Calculating covariance matrices in red, solver in green, and the final beamformer sum in blue. For each step, there is one line for three different choices of temporal averaging, $N_{avg} \in [0, 1, 2]$. (a) 3 beams. (b) 5 beams.}
\label{fig:bench}
\end{figure*}

@@

Present images, both simulated and in-vivo, processed using beamspace Capon and iterative Capon. Comment on the differences between the two and on how much they deviates from the full method.
Show beampatterns for the two compared with the full method. Show executing times for the two methods compared with the full method on the GPU.

@@

@@

>>>>

% *** CITATION PACKAGES ***
%
\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Adaptive Beamforming, Capon Beamformer, Minimum Variance Beamforming, Graphics Processing Unit, GPGPU, Parallel Computing, Ultrasound Imaging.
\end{IEEEkeywords}

@@

%\IEEEPARstart{I}{ntroduction} to Capon adaptive beamforming, ultrasound imaging and GPU/CUDA.
\IEEEPARstart{C}{apon} adaptive beamforming applied in a medical ultrasound setting has recently shown promising results in several studies \cite{Synnevag2007, Austeng2008, Vignon2008, Viola, Mehdizadeh2012}. Although the method introduces some interesting trade-offs in addition to just improved resolution, like maintaining image resolution in combination with higher framerates, smaller probes, or deeper penetration \cite{Synnevag2009}, widespread use has been limited by the tremendous computational complexity associated with the method \cite{So2011}.  In this paper we introduce the first implementation of the Capon beamformer exhibiting real-time performance when applied in a typical cardiac ultrasound setting. To accomplish this task we make use of the massive, and easy accessed, parallel processing power found in modern graphics processing units (GPU's), combined with novel methods to reduce the computational complexity as the problem size grows.

Previous attempts on implementing a parallel Capon beamformer have mainly been focused around radar and passive sonar systems using custom made systolic array processors \cite{McWhirter1989, Moonen1993, Sinha2002}.
%A systolic array processor is custom made hardware, and even if the computational throughput might be higher for selected problems compared with a GPU, the cost related to development and flexibility is considered much higher. 
For medical ultrasound, Chen et al. \cite{Chen2011a, Chen2011} have implemented a Capon beamformer on the GPU that produced real apodization weights from real data. Since a real function is symmetric in frequency space the Capon beamformer is not allowed to shift the main lobe under this constraint, and therefore the full potential is not reached. Shifting the main lobe is an important property of the Capon beamformer in order for it to improve edge definitions and contrast in an ultrasound image. Another aspect of using complex data is the benefits of a lowered sampling rate, keeping the number of samples for a complete image at a minimum. All results in this paper is reported with the use of baseband data.

%Using real data will results in symmetric windows, and even if the number of samples they managed to process per second was high, both the number of floating point operations per sample and the imaging region is reduced using real data compared with use of complex data. It is crucial to use complex data within the Capon beamformer framework, both for reducing the amount of data per image, and to allow for asymmetric windows. All results in this paper is reported with use of critically sampled complex data, both laterally and in range.  (ikke helt kritisk samplet, ikke si det, bare at det er i baseband).

In previous work (cite JOE) we have applied the GPU-based Capon beamformer in an active sonar system. For sonar the real time requirement is much lower than for ultrasound, which means that most array configurations can be handled by a straight forward implementation.
%(Referer til JOE-artikkelen, få med beskrivelse av hva som blir anerledes for ultralyd.)

@@

\subsection{Capon Beamforming}

Bruk riktig terminologi. $N_{avg}$ er K. Antall sub-arrayer må hete noe annet.

Presis på hvilke formler vi skal implementere.

De skal forstå MV etter denne seksjonen.

Ton ned introduksjonen, og sett opp akkurat de ligningene vi implementerer.

(Skriv om den introduserende setningen, start rett på linje to, Kombinere data fra mange sensorer, Leseren kan Ultralyd ikke gpu)

The conventional form of beamforming is delay-and-sum (DAS), where the signal recorded on each element, $x_m[n]$, is delayed to broadside with an appropriate delay $\Delta_m[n]$. The beamformer output, $z[n]$, is then the sum of all $M$ channels weighted with a factor $w_m$,
\begin{align}
z[n] = \sum_{m = 0}^{M-1}w_m^*x_m[n - \Delta_m[n]] = \vec{w}^H\vec{x}[n]. \label{eq:z}
\end{align}
In conventional beamforming, the weighting $\vec{w}$ is usually real, and applied to trade resolution for a better signal-to-noise ratio (SNR). Hence, by increasing the main lobe width of the system while gaining lower side lobe levels.

The basic idea of an adaptive beamformer, as shown in Figure \ref{fig:mvbf}, is to calculate the weights on-the-fly, based on the data at hand, and on a selected optimization criteria in such a way that we minimize interference impinging from other directions than the point of focus. For a complex data vector $\vec{x}[n] \in \mathbb{C}^M$, we have for an adaptive beamformer a data-dependent set of weights, $\vec{w}(\vec{x}[n])$, that when applied on $\vec{x}[n]$ is the best approximation to achieving the selected criteria.

(Vi skal implementer dette. vis bare vektene. Dropp ligning 2, siter, bruk R-hat med en gang. Få med den endelige feilen )

\begin{figure}
\centerline{\includegraphics[width=3in]{gfx/beamforming_mv_lowres.png}}
\caption{Beamforming with adaptive weights $\vec{w}[n]$. Impinging signal is demodulated and aligned in phase by applying steering and focusing delays $\Delta_m[n]$. Capon adaptive weights are then calculated based on the in-phase data, and finally the output is formed by a weighted coherent sum.}
\label{fig:mvbf}
\end{figure}

With the Capon beamformer, adaptive weights are found by solving the following minimization problem \cite{Capon1969}:
\begin{align}
&\min_{\vec{w}} E\{|z[n]|^2\} = \min_{\vec{w}}\vec{w}^H\mat{R}\vec{w}\label{eq:minz}\\
&\text{subjected to } \vec{w}^H\vec{a} = 1,\label{eq:constraint}
\end{align}
where $\mat{R} = E\{\vec{x}[n]\vec{x}[n]^H\}$ is the spatial covariance matrix, and $\vec{a} = \left[ \begin{array}{cccc} e^{-jk_{\tilde{x}}\tilde{x}_0}& e^{-jk_{\tilde{x}}\tilde{x}_1}& ...& e^{-jk_{\tilde{x}}\tilde{x}_{M-1}}\end{array}\right] ^T$ is a far-field steering vector towards angle $\theta = \arcsin(\frac{\lambda k_{\tilde{x}}}{2\pi})$.
Thus, we minimize the output power, while maintaining unit gain in the look direction. The constraint in (\ref{eq:constraint}) is there to avoid the trivial solution $\vec{w} = 0$, and a distorted respons in the direction of $\vec{a}$. The solution to the minimization problem in (\ref{eq:minz}) and (\ref{eq:constraint}) is
\begin{align}\label{eq:w}
\vec{w}[n] = \frac{\mat{R}[n]^{-1}\vec{a}}{\vec{a}^H\mat{R}[n]^{-1}\vec{a}},
\end{align}
where $\vec{a} = [1_0 1_1... 1_{M-1}]^T = \vec{1}$ when $\vec{x}$ is pre-delayed to broadside.

@@

\begin{figure}
\centerline{\includegraphics[width=3in]{gfx/gpu_layout_lowres.png}}
\caption{Calculation of Capon adaptive weights mapped to GPU architecture. A recorded echo across the array for a given range and angle (selected cell) is assigned to a group of $L$ threads that can run independently of all other groups. Note that several samples can be processed per block of threads if $L$ is small. The task of these $L$ threads is to calculate the Capon beamformer output in the three depicted steps.}
\label{fig:gpulayout}
\end{figure}
% Få med at vi processerer hele bildet på en gang. Forklar forskjellen med å prosessere en beam av gangen. Hva med MLA?
% Illustrer tråder og tider for hvordan processeringen går.
% Vi snakker om mottak-stråleformeren.

@@

\subsection{GPU Compute Model}

(Ta med mer banale ting, dette er GPU for ultralydfolk)

Etter denne så må de forstå GPU og hvorfor MV passer.

In this section we briefly discuss the principle behind GPU computing, laying the basis for further discussion on parallel implementation strategies. CUDA by Nvidia has been our choice of GPU developer environment \cite{Nvidia2011}. However, even though CUDA has been used to implement the Capon beamformer, the challenges and proposed methods described in this paper applies for other massive parallel implementation environments as well, like e.g. OpenCL.

@@

\section{Parallel Capon}\label{sec:meth}
As mentioned, widespread use of Capon adaptive beamforming has been limited by its computational complexity. However, if we analyse the beamformer in (\ref{eq:z}) in combination with (\ref{eq:w}) and (\ref{eq:R}), we see that each calculation of a set of Capon weights is independent across the output $z[n]$. As shown in Figure \ref{fig:gpulayout}, a first level of granularity is therefore to divide the image into a grid, where the output in each cell can be calculated independently of all others. Further, based on memory dependencies and to hold memory consumption per thread at a minimum, one should recognise that one block of threads should process at least one output in the final image. Continuing with the calculation of one weight vector, the algorithm can be broken down into three main steps that to some extent can be further divided into a small set of parallel processes. That is, for each data vector $\vec{x}$ in the image:
\begin{align*}
\begin{array}{l}
\text{1) Calculate the sample covariance matrix } \mat{\hat{R}} \text{ as in (\ref{eq:R})}\\
\text{2) Solve the linear system of equations } \mat{\hat{R}}\vec{b} =\vec{ 1}\\
\text{3) Calculate } \vec{w} = \vec{b}/\vec{1}^H\vec{b} \text{ and the amplitude } \vec{w}^H\vec{x}
\end{array}
\end{align*}
%\begin{enumerate}
%\item Calculate the sample covariance matrix $\mat{\hat{R}}$ as in (\ref{eq:R})
%\end{enumerate}
%\begin{enumerate}
%\item[2)] Solve the linear system of equations $\mat{\hat{R}}\vec{b} =\vec{ 1}$
%\end{enumerate}
%\begin{enumerate}
%\item[3)] Calculate $\vec{w} = \vec{b}/\vec{1}^H\vec{b}$ and the amplitude $\vec{w}^H\vec{x}$
%\end{enumerate}
The computational complexity of these three steps is $O(L^3)$, $O(L^3)$, and $O(L)$ respectively if $L = M/2$. For large $L$'s, the first two steps quickly becomes unmanageable, and real time performance can only be achieved by exploring novel solutions to reduce complexity.

%(The three steps have, for modularity, been implemented using three different kernels. Joining all kernels into one could possible lead to an increase in speed.)

@@

\subsection{Calculating Multiple Sample Covariance Matrices}

The straight forward sum in (\ref{eq:R}) has complexity $O(L^2KN) = O(L^3)$ if the number of subarrays $K$ is small. This is actually the same as for inverting a $L \times L$ matrix. However, little attention has been devoted to this step in the literature until now. Note that for a typical array configuration we typically smooth more in space than in range. Hence, N is usually small compared to $K$. For short subarrays the construction of $\mat{\hat{R}}$ is dominated by the number of elements $M$, since $K = M - L + 1$. From (\ref{eq:R}) it is obvious that calculation of one element in $\mat{\hat{R}}$ is independent of all the others. A natural level of granularity would then be to assign one thread to each element of $\mat{\hat{R}}$. This will minimize global reads and writes needed per thread, but unfortunately the maximum number of threads per block puts an upper limit on subarray length $L$, $L_{max}=32$, if we want to avoid block-to-block synchronization.

@@

Skriv om utfordringene om å lage en solver på GPU. Ikke dra inn UHDU.

@@

%\subsection{Iterative Capon}
%The idea behind iterative Capon is to perform Capon using small subarrays in several iterations until there is only two subarrays to sum. In this way we fix the size of L, hence the complexity of solving $\mat{R}\vec{b} = \vec{1}$. However, for each iteration we re-obtain L-1 degrees of freedom until all are retrieved after $K = M-L+1$ iterations. Since subarray averaging has been applied to decorrelated the signal, we might loose this effect when reestablishing all degrees of freedom. The number of iterations should therefore be restricted to $K/2$ to equal the normal choice of $L = M/2$ when it comes to degrees of freedom.

@@

% stolpediagram, med de ulike metodenes kjøretid oppehverandre.

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_us_32_lr.png} \label{fig:benchUS32}}
\hfil
\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_us_64_lr.png}%
\label{fig:benchUS64}}}
\caption{(Change into bar plot?) Benchmark of GPU Capon beamforming for a cardiac image covering a 70 degrees sector. Execution time is plotted as a function of subarray length $L$. The plot shows execution times for the three steps listed in Section \ref{sec:meth}. Calculating covariance matrices in red, solver in green, and the final beamformer sum in blue. For each step, there is one line for three different choices of temporal averaging, $N_{avg} \in [0, 1, 2]$. (a) A 32 elements array. (b) A 64 elements array.}
\label{fig:bench}
\end{figure*}

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_us_32_lr.png} \label{fig:benchBS3}}
\hfil
\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_us_64_lr.png}%
\label{fig:benchBS5}}}
\caption{(TODO: Add the right figure. Change it into a bar plot?) Benchmark of GPU Beamspace Capon beamforming for a cardiac image covering a 70 degrees sector. Execution time is plotted as a function of number of elements $M$. The plot shows execution times for the three steps listed in Section \ref{sec:meth}. Calculating covariance matrices in red, solver in green, and the final beamformer sum in blue. For each step, there is one line for three different choices of temporal averaging, $N_{avg} \in [0, 1, 2]$. (a) 3 beams. (b) 5 beams.}
\label{fig:benchBS}
\end{figure*}

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=2in]{gfx/mv_phantom.png} \label{fig:phantomDAS}}
\hfil
\subfloat[]{\includegraphics[width=2in]{gfx/mv_phantom.png} \label{fig:phantomMV}}
\hfil
\subfloat[]{\includegraphics[width=2in]{gfx/mv_phantom.png} \label{fig:phantomBS}}}
\caption{(TODO: Add the right figures) Have graph showing cyst contrast as a function of different parameters instead? Cyst and point targets phantom a) Delay-and-sum, uniform weights. b) Capon ($M=?, L=?, N=?$) c) Beamspace Capon ($M=?, L=?, N=?, N_b=?$).}
\label{fig:bench}
\end{figure*}

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=2in]{gfx/us_image.png} \label{fig:phantomDAS}}
\hfil
\subfloat[]{\includegraphics[width=2in]{gfx/us_image.png} \label{fig:phantomMV}}
\hfil
\subfloat[]{\includegraphics[width=2in]{gfx/us_image.png} \label{fig:phantomBS}}}
\caption{(TODO: Add the right figures) Have graph showing cavity-wall contrast as a function of parameters instead? In-vivo cardiac ultrasound image a) Delay-and-sum, uniform weights. b) Capon ($M=?, L=?, N=?$) c) Beamspace Capon ($M=?, L=?, N=?, N_b=?$).}
\label{fig:bench}
\end{figure*}

@@

Present images, both simulated and in-vivo, processed using beamspace Capon. Comment on the differences between the two and on how much they deviates from the full method.
%Show beampatterns for the two compared with the full method. 
Show executing times for the two methods compared with the full method on the GPU.

@@

Ta med en serie med bilde. Må vise tydelig at det gir forbedring.

@@

Toeplitz-based solver (cite new article). Discuss it.
